Generating urban morphologies at large scales

### 2019-03-15 paper.tex
.

We obtain a broad variety of forms, measures such as the Moran index

We can produce a typology of sampled urban areas through these measures.
% TODO typology of urban areas ?

>>>>

%     moran          avgDistance        density         components      avgDetour        avgBlockArea  
% Min.   :0.01881   Min.   :0.2120   Min.   :0.0504   Min.   :  7.0   Min.   : 0.1165   Min.   :  4.0  
% 1st Qu.:0.07658   1st Qu.:0.6630   1st Qu.:0.0984   1st Qu.: 60.0   1st Qu.: 4.6543   1st Qu.: 10.0  
% Median :0.10421   Median :0.8022   Median :0.1860   Median :109.0   Median : 6.9233   Median : 12.0  
% Mean   :0.11659   Mean   :0.7586   Mean   :0.2193   Mean   :126.9   Mean   : 7.7544   Mean   : 14.8  
 %3rd Qu.:0.14063   3rd Qu.:0.8870   3rd Qu.:0.3120   3rd Qu.:184.0   3rd Qu.:10.1821   3rd Qu.: 16.0  
% Max.   :0.93934   Max.   :1.1405   Max.   :0.7980   Max.   :413.0   Max.   :26.3172   Max.   :143.0  
% avgComponentArea fullDilationSteps fullErosionSteps
% Min.   :  5.00   Min.   : 3        Min.   : 1.000  
% 1st Qu.: 30.00   1st Qu.:16        1st Qu.: 3.000  
% Median : 54.00   Median :26        Median : 4.000  
% Mean   : 60.32   Mean   :28        Mean   : 4.049  
% 3rd Qu.: 86.00   3rd Qu.:38        3rd Qu.: 5.000  
% Max.   :183.00   Max.   :80        Max.   :21.000

We obtain a broad variety of forms, measures such as the Moran index varying between 0.02 (small disparate settlements) to 0.93 (one huge block), with a median at 0.10 (several medium size buildings). Similarly, the number of dilation steps varies from 3 (narrow streets only) to 80 (mostly open spaces) with a median at 26. The mean density is 0.21, what means that around 21\% of the soil is covered with building in average in the space we sampled, confirming that the most of urban areas are not dense contrary to the highly dense centers which are a minority.

We can also consider the distribution of these measures within sampled urban areas.
